Overt attentional capture by reward-related stimuli overcomes inhibitory suppression

### 2019-04-26 README.Rmd
updated with github pat
updated Readme and minor paper changes

> Pearson, D., Watson, P., Cheng, P., Most, S. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (`r format(Sys.Date(), "%Y")`. Investigating attentional suppression of reward-related distractors. Retrieved from <https://osf.io/yrdzv>

@@

>>>>

> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (`r format(Sys.Date(), "%Y")`). Investigating attentional suppression of reward-related distractors. Retrieved from <https://osf.io/yrdzv>

@@

Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.Rmd](analysis/analysis_report.Rmd) to produce a report containing all statistical analyses contained in our preprint. You can also knit [paper.Rmd](analysis/paper/paper.Rmd) to produce a reproducible copy of the preprint.

This compendium is still a work in progress, with Docker integration planned for the future.

### 2019-04-26 analysis/paper/paper.Rmd
updated Readme and minor paper changes

# Introduction
When we interact with the world, our visual attention system can prioritise important information. For example, when driving towards an intersection, we can selectively attend to a stop sign on a busy street. Sometimes, however, we may find that stimuli that are irrelevant to our current task may nevertheless capture our attention in a seemingly automatic and involuntary way (e.g., a flashing alert, or colourful billboard). Consistent with this framework, an influential view of attentional selection has drawn a distinction between two forms of attentional control: one that is volitional and goal directed (top-down control) and another that is automatic and stimulus driven [@Yantis2000]. However, exactly how these two processes interact has been the subject of extensive debate.

@@

Recently, a hybrid model of attentional selection has been proposed---the *signal suppression hypothesis* [@Gaspelin2018; @Sawaki2010]---which attempts to integrate these two competing accounts. According to this model, salient stimuli automatically generate an attentional priority signal (or "attend-to-me" signal) that will go on to capture attention unless it is suppressed by an inhibitory control process, which builds over repeated experience with the salient stimulus [@Gaspelin2018b]. This account is consistent with stimulus-driven theories, in that it proposes that physically salient stimuli have the potential to involuntarily capture attention; however it is also consistent with goal-directed theories in that it proposes that there is some top-down control of the allocation of attention. Evidence supporting the signal suppression hypothesis has largely come from the event-related potential (ERP) literature [for review, see @Gaspelin2018a], however recent studies have demonstrated behavioural evidence of suppression in the context of overt attention [i.e., eye-movements: see @Gaspelin2016; @Gaspelin2018b; @Ipata2006] and covert attention [i.e., shifts of attention that are not accompanied by eye-movements: see @Gaspelin2015].

@@

Statistical analyses were conducted in `r cite_r()` with the afex package  [@R-afex] used to calculate ANOVAs and the emmeans package [@R-emmeans] for follow-up contrasts. Greenhouse-Geisser corrections are reported where appropriate. In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor]. Bayes
factors are interpreted in line with the guidelines suggested by @Jeffreys1961. Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@marwick2018] are available at https://osf.io/yrdzv/.

>>>>

# Introduction
When we interact with the world, our visual attention system can prioritise important information. For example, when driving towards an intersection, we can selectively attend to a stop sign on a busy street. Sometimes, however, we may find that stimuli that are irrelevant to our current task nevertheless capture our attention in a seemingly automatic and involuntary way (e.g., a flashing alert, or colourful billboard). Consistent with this framework, an influential view of attentional selection has drawn a distinction between two forms of attentional control: one that is volitional and goal directed (top-down control) and another that is automatic and stimulus driven [@Yantis2000]. However, exactly how these two processes interact has been the subject of extensive debate.

@@

Recently, a hybrid model of attentional selection has been proposed---the *signal suppression hypothesis* [@Gaspelin2018; @Sawaki2010]---which attempts to integrate these two competing accounts. According to this model, salient stimuli automatically generate an attentional priority signal (or "attend-to-me" signal) that will go on to capture attention unless it is suppressed by an inhibitory control process, which builds over repeated experience with the salient stimulus [@Gaspelin2018b]. This account is consistent with stimulus-driven theories, in that it proposes that physically salient stimuli have the potential to involuntarily capture attention; however it is also consistent with goal-directed theories in that it proposes that there is some top-down control of the allocation of attention. Evidence supporting the signal suppression hypothesis has largely come from the event-related potential (ERP) literature [for review, see @Gaspelin2018a], however recent studies have demonstrated behavioural evidence of suppression in the context of overt attention [i.e., eye-movements: see @Gaspelin2018b; @Gaspelin2016; @Ipata2006] and covert attention [i.e., shifts of attention that are not accompanied by eye-movements: see @Gaspelin2015].

@@

Statistical analyses were conducted in `r cite_r()` with the afex package  [@R-afex] used to calculate ANOVAs and the emmeans package [@R-emmeans] for follow-up contrasts. Greenhouse-Geisser corrections are reported where appropriate. In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor]. Bayes
factors are interpreted in line with the guidelines suggested by @Jeffreys1961. Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@R-rrtools] are available at https://osf.io/yrdzv/.

### 2019-04-26 analysis/paper/paper.tex
updated Readme and minor paper changes

When we interact with the world, our visual attention system can
prioritise important information. For example, when driving towards an
intersection, we can selectively attend to a stop sign on a busy street.
Sometimes, however, we may find that stimuli that are irrelevant to our
current task may nevertheless capture our attention in a seemingly
automatic and involuntary way (e.g., a flashing alert, or colourful
billboard). Consistent with this framework, an influential view of
attentional selection has drawn a distinction between two forms of
attentional control: one that is volitional and goal directed (top-down
control) and another that is automatic and stimulus driven (Yantis,
2000). However, exactly how these two processes interact has been the
subject of extensive debate.

@@

Recently, a hybrid model of attentional selection has been
proposed---the \emph{signal suppression hypothesis} (Gaspelin \& Luck,
2018b; Sawaki \& Luck, 2010)---which attempts to integrate these two
competing accounts. According to this model, salient stimuli
automatically generate an attentional priority signal (or
\enquote{attend-to-me} signal) that will go on to capture attention
unless it is suppressed by an inhibitory control process, which builds
over repeated experience with the salient stimulus (Gaspelin \& Luck,
2018a). This account is consistent with stimulus-driven theories, in
that it proposes that physically salient stimuli have the potential to
involuntarily capture attention; however it is also consistent with
goal-directed theories in that it proposes that there is some top-down
control of the allocation of attention. Evidence supporting the signal
suppression hypothesis has largely come from the event-related potential
(ERP) literature (for review, see Gaspelin \& Luck, 2019), however
recent studies have demonstrated behavioural evidence of suppression in
the context of overt attention (Gaspelin \& Luck, 2018a; i.e.,
eye-movements: see Gaspelin, Leonard, \& Luck, 2017; Ipata, Gee,
Gottlieb, Bisley, \& Goldberg, 2006) and covert attention (i.e., shifts
of attention that are not accompanied by eye-movements: see Gaspelin,
Leonard, \& Luck, 2015).

@@

Statistical analyses were conducted in R (Version 3.5.1; R Core Team,
2018) with the afex package (Singmann, Bolker, Westfall, \& Aust, 2018)
used to calculate ANOVAs and the emmeans package (Lenth, 2018) for
follow-up contrasts. Greenhouse-Geisser corrections are reported where
appropriate. In cases where a conclusion is drawn on the basis of a null
effect, we report the Bayes factor that corresponds to a Bayesian
\emph{t}-test using the default Cauchy prior, conducted using the
BayesFactor package (Morey \& Rouder, 2018).

@@

>>>>

When we interact with the world, our visual attention system can
prioritise important information. For example, when driving towards an
intersection, we can selectively attend to a stop sign on a busy street.
Sometimes, however, we may find that stimuli that are irrelevant to our
current task nevertheless capture our attention in a seemingly automatic
and involuntary way (e.g., a flashing alert, or colourful billboard).
Consistent with this framework, an influential view of attentional
selection has drawn a distinction between two forms of attentional
control: one that is volitional and goal directed (top-down control) and
another that is automatic and stimulus driven (Yantis, 2000). However,
exactly how these two processes interact has been the subject of
extensive debate.

@@

Recently, a hybrid model of attentional selection has been
proposed---the \emph{signal suppression hypothesis} (Gaspelin \& Luck,
2018b; Sawaki \& Luck, 2010)---which attempts to integrate these two
competing accounts. According to this model, salient stimuli
automatically generate an attentional priority signal (or
\enquote{attend-to-me} signal) that will go on to capture attention
unless it is suppressed by an inhibitory control process, which builds
over repeated experience with the salient stimulus (Gaspelin \& Luck,
2018a). This account is consistent with stimulus-driven theories, in
that it proposes that physically salient stimuli have the potential to
involuntarily capture attention; however it is also consistent with
goal-directed theories in that it proposes that there is some top-down
control of the allocation of attention. Evidence supporting the signal
suppression hypothesis has largely come from the event-related potential
(ERP) literature (for review, see Gaspelin \& Luck, 2019), however
recent studies have demonstrated behavioural evidence of suppression in
the context of overt attention (i.e., eye-movements: see Gaspelin \&
Luck, 2018a; Gaspelin, Leonard, \& Luck, 2017; Ipata, Gee, Gottlieb,
Bisley, \& Goldberg, 2006) and covert attention (i.e., shifts of
attention that are not accompanied by eye-movements: see Gaspelin,
Leonard, \& Luck, 2015).

@@

Statistical analyses were conducted in R (Version 3.5.1; R Core Team,
2018) with the afex package (Singmann, Bolker, Westfall, \& Aust, 2018)
used to calculate ANOVAs and the emmeans package (Lenth, 2018) for
follow-up contrasts. Greenhouse-Geisser corrections are reported where
appropriate. In cases where a conclusion is drawn on the basis of a null
effect, we report the Bayes factor that corresponds to a Bayesian
\emph{t}-test using the default Cauchy prior, conducted using the
BayesFactor package (Morey \& Rouder, 2018). Bayes factors are
interpreted in line with the guidelines suggested by Jeffreys (1961).
Experiment scripts, raw data, and a reproducible research compendium of
analysis scripts (Marwick, 2019) are available at
\url{https://osf.io/yrdzv/}.

@@

\hypertarget{ref-R-rrtools}{}
Marwick, B. (2019). \emph{Rrtools: Creates a reproducible research
compendium}. Retrieved from \url{https://github.com/benmarwick/rrtools}
